### 2025-01-13 sections/3-datasets.tex
added most of the plots
added language for how we check recall

@@

As another example of an exotic distance function, we benchmarked CAKES on the RadioML dataset~\cite{oshea2018radioml}.
The RadioML dataset contains samples of synthetically generated signal captures of different modulation modes over a range of SNR levels.
Specifically, it comprises 24 modulation modes at 26 different signal-to-noise ratio (SNR) levels ranging from -20 dB to 30 dB, with 4,096 samples at each combination of modulation mode and SNR level.
Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total.
Each sample is a 1,024-dimensional complex-valued vector, representing a signal capture (a time-series of complex-valued numbers).
We used a subset of this dataset, containing 97,920 samples at 10dB SNR and used the other 8,576 samples at 10dB SNR as a hold-out set of queries.
We use Dynamic Time Warping~\cite{muller2007dynamic} as the distance function for this dataset.

>>>>

In order to calculate recall on the augmented datasets, we perform linear search in Rust and save the results to disk.
We verified that linear search on the original dataset produced neighbors with perfect recall compared to those provided by the ANN-Benchmarks suite.
We then use the results of linear search on the augmented datasets as ground truth for calculating recall of CAKES's algorithms in Rust and read them in Python for calculating recall of HNSW, ANNOY, and FAISS-IVF.

@@

As another example of an exotic distance function, we benchmarked CAKES on the RadioML dataset~\cite{oshea2018radioml}.
The RadioML dataset contains samples of synthetically generated signal captures of different modulation modes over a range of SNR levels.
Specifically, it comprises 24 modulation modes at 26 different signal-to-noise ratio (SNR) levels ranging from -20 dB to 30 dB, with 4,096 samples at each combination of modulation mode and SNR level.
Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total.
Each sample is a 1,024-dimensional complex-valued vector, representing a signal capture (a time-series of complex-valued numbers).
We used a subset of this dataset, containing $97,304$ samples at 10dB SNR and used another $1,000$ samples at the same SNR as a hold-out set of queries.
We use Dynamic Time Warping~\cite{muller2007dynamic} as the distance function for this dataset.
